---
title: "Services"
author: "David Yang"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
library(pacman)
library(tidyverse)
pacman::p_load(tidyverse,readxl)
pacman::p_load_current_gh("hathawayj/buildings")
```

```{r load_data}
dat <- buildings0809 %>% 
  inner_join(climate_zone_fips, by = c("FIPS.county","FIPS.state"))
```

## Prep Data Wrangling

```{r}
not_restaurants <- 
  c("development","Food preperation center", "Food Services center","bakery",
    "Grocery","conceession","Cafeteria", "lunchroom","school","facility"," hall ") %>% 
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

standalone_retail <- 
  c("Wine","Spirits","Liquor","Convenience","drugstore","Flying J", "Rite Aid ",
    "walgreens ","Love's Travel ") %>% 
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

full_service_type <- 
  c("Ristorante","mexican","pizza ","steakhouse"," grill ","buffet","tavern",
    " bar ","waffle","italian","steak house") %>% 
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

quick_service_type <- 
  c("coffee"," java "," Donut ","Doughnut"," burger ","Ice Cream ","custard ",
    "sandwich ","fast food "," bagel ") %>% 
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

quick_service_names <- 
  restaurants$Restaurant[restaurants$Type %in% c("coffee","Ice Cream","Fast Food")] %>%
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

full_service_names <- 
  restaurants$Restaurant[restaurants$Type %in% c("Pizza","Casual Dining","Fast Casual")] %>% 
  str_to_lower() %>% 
  unlist() %>% 
  str_trim() %>% 
  str_flatten(collapse = "|")

CS6 <- dat %>%
  filter(Type == "Food_Beverage_Service") %>% 
  mutate(Food = case_when(ProjectTitle %>%
                            str_to_lower() %>% 
                            str_detect(not_restaurants) ~ "not restaurants",
                          ProjectTitle %>% 
                            str_to_lower() %>% 
                            str_detect(standalone_retail) ~ "standalone retail",
                          ProjectTitle %>% 
                            str_to_lower() %>% 
                            str_detect(full_service_type) ~ "full service type",
                          ProjectTitle %>% 
                            str_to_lower() %>% 
                            str_detect(quick_service_type) ~ "quick service type",
                          ProjectTitle %>% 
                            str_to_lower() %>% 
                            str_detect(quick_service_names) ~ "quick service type",
                          ProjectTitle %>% 
                            str_to_lower() %>% 
                            str_detect(full_service_names) ~ "full service type",
                          SqFt >= 4000 ~ "full service type",
                          SqFt < 4000 ~ "quick service type",
                          TRUE ~ "Other")) 
Q1 <- CS6 %>% 
  filter(Food %in% c("full service type", "quick service type")) %>%
  group_by(County.x, Year, Food, Month) %>%
  summarise(count = n()) %>%
  group_by(County.x, Year, Food) %>% 
  mutate(sum = cumsum(count))  %>% 
  select(count, sum, County.x, Year, Month, Food) %>% 
  unite("Time",Year,Month,sep = "")

Q1$Time <- as.numeric(Q1$Time)
```

## Question 1 
How did full-service restaurant construction compare to quick service restaurant construction across county and years?  
How to make the graph replace the NA?

```{r Visualization}
Q1 %>% 
  ggplot(aes(x = Time, y = sum, group = Food, color = Food)) +
  facet_wrap(~County.x, nrow = 2) +
  geom_line(aes(x = Time, y = sum)) +
  geom_point(aes(x = Time, y = sum)) +
  theme_bw()
```

## Question 2,3,4
How did restaurant construction fare compare to the other commercial construction in Idaho?  
Which county in Idaho spent the most on fast food construction each year?  
In that county how did other commercial construction compare?

#### Q2 Wrangling

```{r tidy_data}
Q2 <- CS6 %>% 
  unite("Time", Year, Month,sep = "") %>% 
  mutate(Class = case_when(
    Food == "not restaurants" ~ "Other service", TRUE ~ "Restaurant")) %>% 
  group_by(County.x, Food, Time, Class) %>%
  mutate(count = n()) %>%
  group_by(count, County.x, Food, Time, Class) %>% 
  mutate(sum = cumsum(count))  %>% 
  ungroup() %>% 
  select(count, sum, County.x, Time, Food, Class)

view(Q2)

Q2 %>% 
  ggplot(aes(x = Time, y = sum, group = Class, color = Class)) +
  facet_wrap(~County.x, nrow = 2) +
  geom_line(aes(x = Time, y = sum)) +
  geom_point(aes(x = Time, y = sum)) +
  theme_bw() 
```


